---
title: "shopScrape Vinette"
author: "Mariah Barnes"
output: rmarkdown::html_vignette
desctiption: This package is created for price analysis of shopping sites. In this package will be data frame, currency, and parsing functions for webscrapping. 
vignette: >
  %\VignetteIndexEntry{shopScrape Vinette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shopscrape)
```
##Installation
Run the command
```
Install.packages("shopscrape)
```
## Functions
  * `shopScrape()` scrapes data and puts it in interactive table.
  Allows you to search the table and find relatable items and compare prices.
```{r}
shopScrape("https://www.thereformation.com/categories/new?gclid=CjwKCAiAm7OMBhAQEiwArvGi3EYt2jozZbzQktEYy2iInclcxHpJKKnWfqu3Jo2mHfABJ-R90ghQVhoCmwAQAvD_BwE" , ".product-prices__price span , .product-summary__name a","https://www.zara.com/us/en/woman-must-haves-l4503.html?v1=1609213", ".price__amount-current , #main .link span")
```
  
  * `basicPrice()` scraped price node and put it in basic histogram .
  
  * `currencyFunc()` changes currency values from USD, Peso, and Euro.
```{r}
currencyFunc(usd= 2.78)
```
  
  * `priceAna()` scrapes prices and turn category means into histogram. 
```{r}
priceAna("https://www.thereformation.com/categories/new?gclid=CjwKCAiAm7OMBhAQEiwArvGi3EYt2jozZbzQktEYy2iInclcxHpJKKnWfqu3Jo2mHfABJ-R90ghQVhoCmwAQAvD_BwE" , ".product-prices__price span , .product-summary__name a")
```
  
  * `priceNum()` scrapes prices and turns them into numerical values.

   
  * `samelNa()` changes the number of the rows and add NA's to get two lists of same length.
  
```{r}
x<- c(1:10)
y<- c(1:9)

samelNA(x,y)
```
  
