---
title: "shopScrape Vinette"
author: "Mariah Barnes"
output: rmarkdown::html_vignette
desctiption: This package is created for price analysis of shopping sites.The motivation behind it is the problems that shoppers face when looking at two different sites and wanting to easily compare the prices. In this package will be ways to compare prices in a data frame while also searching the table. Other functions includes webscrapping for price barplots, currency changes, and parsing numbers. This can be used for big shoppping events like black Friday or evn better cyber Monday.In the future I would like to update thr currency function to take in more currencies and update the functionality of the barplots. 
vignette: >
  %\VignetteIndexEntry{shopScrape Vinette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shopscrape)
```
##Installation
Run the command
```
Install.packages("shopscrape)
```
## Functions
  * `shopScrape()` scrapes data and puts it in interactive table.
  Allows you to search the table and find relatable items and compare prices.
```{r}
shopScrape("https://www.thereformation.com/categories/new?gclid=CjwKCAiAm7OMBhAQEiwArvGi3EYt2jozZbzQktEYy2iInclcxHpJKKnWfqu3Jo2mHfABJ-R90ghQVhoCmwAQAvD_BwE" , ".product-prices__price span , .product-summary__name a","https://www.zara.com/us/en/woman-must-haves-l4503.html?v1=1609213", ".price__amount-current , #main .link span")
```
  
  * `basicPrice()` scraped price node and put it in basic histogram .
  
  * `currencyFunc()` changes currency values from USD, Peso, and Euro.
```{r}
currencyFunc(usd= 2.78)
```
  
  * `priceAna()` scrapes prices and turn category means into histogram. 
```{r}
priceAna("https://www.thereformation.com/categories/new?gclid=CjwKCAiAm7OMBhAQEiwArvGi3EYt2jozZbzQktEYy2iInclcxHpJKKnWfqu3Jo2mHfABJ-R90ghQVhoCmwAQAvD_BwE" , ".product-prices__price span , .product-summary__name a")
```
  
  * `priceNum()` scrapes prices and turns them into numerical values.

   
  * `samelNa()` changes the number of the rows and add NA's to get two lists of same length.
  
```{r}
x<- c(1:10)
y<- c(1:9)

samelNA(x,y)
```
  
